---
title: "Krogers_Metaheuristics_assignment"
output: html_document
---
```{r}
library(GenSA)
library(ggplot2)
library(GA)
```

The following code will load the tickers/stock names and establish a date range. 

```{r}
library("quantmod")
tickers <- c("GE", "IBM", "JPM", "MSFT", "WMT")
getSymbols(tickers, from = "2000-12-01", to = "2010-12-31")
P <- NULL
for(ticker in tickers) {
 tmp <- Cl(to.monthly(eval(parse(text = ticker))))
 P <- cbind(P, tmp)
}
colnames(P) <- tickers
R <- diff(log(P))
R <- R[-1,]
mu <- colMeans(R)
sigma <- cov(R)
library("PerformanceAnalytics")
pContribCVaR <- ES(weights = rep(0.2, 5), method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)$pct_contrib_ES
obj <- function(w) {
 fn.call <<- fn.call + 1
 if (sum(w) == 0) { w <- w + 1e-2 }
 w <- w / sum(w)
 CVaR <- ES(weights = w, method = "gaussian", portfolio_method = "component", mu = mu, sigma = sigma)
 tmp1 <- CVaR$ES
 tmp2 <- max(CVaR$pct_contrib_ES - 0.225, 0)
 out <- tmp1 + 1e3 * tmp2
 return(out)
}
```

Applying a Genetic algorithm, Comparing GA to Simulated annealing

```{r}
set.seed(1234)
fn.call <<- 0
out.GenSA <- GenSA(fn = obj, lower = rep(0, 5), upper = rep(1, 5), control = list(smooth = FALSE, max.call = 3000))
fn.call.GenSA <- fn.call
out.GenSA$value
out.GenSA$counts
cat("GenSA call functions", fn.call.GenSA, "times.\n")
wstar.GenSA <- out.GenSA$par
wstar.GenSA <- wstar.GenSA / sum(wstar.GenSA)
rbind(tickers, round(100 * wstar.GenSA, 2))
100 * (sum(wstar.GenSA * mu) - mean(mu))
```


```{r}
gap_2 <- ga( type= "real-valued", fitness = function(w) - obj(w), lower = rep(0,5), upper = rep(1, 5), popSize = 50)
summary(gap_2)
plot(gap_2)
```


Creating a dataset label "x" and "y" 
```{r}
x <- c(61,63,67,69,70,74,76,81,86,91,95,97)
y <- c(4.28,4.08,4.42,4.17, 4.48,4.3,4.82,4.7,5.11,5.13,5.64,5.56)
fun =function(x,y) {(sin(10*x)*cos(10*y)+2)/sqrt(x^4+y^4+1)}
obj = function(z)

plot(x,y)
```

Plotting the numbers in a graph to get a visual representation of the dataset plots.

```{r}
plot(x,y)
```


```{r}
ssyy <- sum((y-mean(y)) ^ 2)
ssxy <- sum (( x -mean (x))* (y-mean(y)))
ssx <- sum((x-mean(x))^ 2)
b1 <- ssxy/ssx
b0 <- mean(y) - b1 * mean(x)

b1 
b0
```

```{r}
linear_model <- lm(y ~ x)
summary(linear_model)
```

```{r}
obj <- function (r) {
  fn <- function (b0, b1) {
    return (sum(y-(b0+b1*x))^2)
    
  }
  return (fn(r[1], r[2]))
}

upperbound <- c(2,1)
lowerbound <- c(0,0)

```

Genetic Algorithm

```{r}
ga_lookup <- ga(type = "real-valued", fitness = function(x)- obj(x), lower = lowerbound, upper=upperbound, popSize = 50
              
)
summary(ga_lookup)
plot(ga_lookup)
```

simulate Anealing

```{r}
par <- c(1,0)
sa_lookup <- GenSA(par = par, lower=lowerbound, upper= upperbound, fn=obj)
```



```{r}
set.seed(1234)
fn.call <<- 0
out.GenSA <- GenSA(fn = obj, lower =rep (0,2), upper =rep(5,2), control = list (smooth = F, max.call=3000))
fn.call.GenSA <- fn.call
out.GenSA$value
out.GenSA$counts
cat("GenSa call funtions", fn.call.GenSA, "times.\n")
```

plotting my solution and labeling the outputs on the graph.

```{r}
gap <- ga(type = "real-valued",fitness=obj, lower =rep(0, 2), upper =rep(5, 2), popSize =50, maxiter =150)
summary(gap)
plot(gap)
```


Side Project.......

plotting a ggplot for 
a) Regression Line of Gentic Algorritm (Ga)
b) Genetic Algoritm (GA)
c) Simulated Anealing (SA)


```{r}
library(ggplot2)

dataset <- data.frame(x,y)
ggplot(dataset, aes(x = x, y =y)) + 
  ggtitle( 
    "Regression Line of Gentic Algorritm (Ga), Genetic Algoritm(GA),Simulated Anealing", subtitle = "A comparison between GA, SA and LM") +
  geom_point(shape=1) +
  geom_smooth(method=lm, se=FALSE, col = "green") +
  
    geom_abline(intercept = sa_lookup$par[1],
      slope = sa_lookup$par[2],
      col = "red") +
  
  geom_abline( intercept = ga_lookup@solution[1],
   slope = ga_lookup@solution[2],
   col = "orange") +
 
geom_text(aes(
  x=70,
  y=5.1,
  label = sprintf("GA -> y= %g + %g * x", sa_lookup$par[1], sa_lookup$par[2]),
  color="GA"
))+
  geom_text(aes(
    x=70,
    y=5.3,
    label =sprintf("LM -> y = %g + %g * x", b0, b1), color= "LM"
  )) +
  geom_text(aes(
    x=70,
    y=5.5,
    label = sprintf("SA -> y = %g + %g * x", sa_lookup$par[1], sa_lookup$par[2]), color ="SA"
  ))

```


